INTELLIGENT SYSTEMS

### 2021-03-15 slides.tex
layout slides
start paper1

\documentclass{beamer}
\usepackage{graphicx}

\title[short]{INTELLIGENT SYSTEMS}
\author{Flavio Forenza}\vspace{10pt}
\institute{mat. 938367}

\date{}

\usetheme{Darmstadt}
\begin{document}

\begin{frame}
    \maketitle
    \begin{center}
        \includegraphics[width = 0.4\linewidth ]{images/logoUnimi.png}   
    \end{center}
\end{frame}

\begin{frame}
    %\frametitle{Roadm}
    ciao  
\end{frame}

>>>>

\documentclass{beamer}
\usepackage{graphicx}
\graphicspath{{images/}}

\setbeamertemplate{footline}[frame number]
\setbeamertemplate{page number in head/foot}[appendixframenumber]

\usetheme{Darmstadt}

\title[short]{INTELLIGENT SYSTEMS}
\author[Flavio Forenza]{Flavio Forenza \\ \tiny flavio.forenza@studenti.unimi.it\\[5mm] \includegraphics[scale = 0.06]{logoUnimi2.png}}
\institute{Department of Computer Science,\\ University of Milan, Italy}
\date{\tiny \today}

\begin{document}

\begin{frame}
    \maketitle
\end{frame}

\logo{\includegraphics[width=0.1\linewidth]{logoUnimi2.png}}
\section{Paper 1}
\subsection{\emph{"A Unified Framework for Salient StructureDetection by Contour-Guided Visual Search"}}
\begin{frame}
    \frametitle{INTRODUCTION}

\end{frame}
